EUC_PVE

### 2014-10-31 markdowns/master.rmd
added more plots to markdown

### seedling predawn and midday water potentials

@@

Predicted responses of Amax on a mass basis to leaf starch and N levels
```{r AmassvsTNCandN}
source("master_scripts/photochem_predict.R")
```

>>>>

seedling predawn and midday water potentials

@@

Predicted responses of Amax on a mass basis to leaf starch and N levels
```{r AmassvsTNCandN}
source("master_scripts/Amax_TNC_N_plotting.R")
```

Mass allocaiton and LMF plotting
```{r Harvest allocation and LMF}
source("master_scripts/allocation_plotting.R")
```
